Wu-Tang Clan

### 2015-03-20 rmtw/a6/latex8.tex
added case compnay description a6

% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
% 		\textsuperscript{*x} Computer Science and Engineering  \\
% 		\textsuperscript{*x}University of Gothenburg }
\author{John Burchell \qquad William Granli \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
		Computer Science and Engineering  \\
		University of Gothenburg }

@@

\section{Case Company Description}
The case company is a 
Mention the country, size and domain. 
In domain of surveillance cameras and they develop embedded software for the cameras. 
Focus mostly on the API since that's what's relevant to our study. 
Something about market leader in their domain - and that means that changes to their API could have large consequences.

Also try to get some information on the users of the API. (it might be relevant). %%Not sure if we can get htat now, maybe thorugh the interviews or by asking Imed

@@

%%Add why we didn't use other sampling methods for the final handin.

\section{Methodology}
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. The goal of the study was twofold. Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]

@@

We have structured our research around three major steps. Initially, the study was planned. Following that, we collected the data and lastly, we analysed the data.

\subsection{Case Study Design and Planning}

not sure if we will need this as a section
*Do we create a case study protocol or is it too early?

>>>>

% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
% 		\textsuperscript{*x} Computer Science and Engineering  \\
% 		\textsuperscript{*x}University of Gothenburg }

\author{John Burchell \qquad William Granli \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
		Computer Science and Engineering  \\
		University of Gothenburg }

@@

\section{Case Company Description}
The case company is a medium-sized company in the domain of security cameras. The company has its headquarters in Lund, Sweden, but it operates worldwide. The company is the global market leader in the markets of network cameras and video encoders. The company develops embedded software for the security cameras, and some cameras are designed to be accessible by APIs that are also developed by the company.

%Try to get information about the users of the API. Either through Imed, or through the interviews.

@@

%Try to motivate why other sampling methods weren't used.

\section{Methodology}
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. The goal of the study was twofold. Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]

@@
